Revealing transient strain in geodetic data with Gaussian process regression

### 2017-10-23 RevisedSubmission/hines_hetland_2017_gji.tex
did more

We provide an example to give the prior on transient displacements a
more tangible meaning. we can use a squared exponential function for
$X_i$ and $T_i$,

\begin{equation}\label{eq:ExampleCov}
X_i(\pos,\pos') = \exp\left(\frac{-||\pos - \pos'||_2^2}{2\ell^2}\right), \ \ \ \ 
T_i(t,t') = \phi^2 \exp\left(\frac{-|t - t'|^2}{2\tau^2}\right),
\end{equation}

which satisfies our requirements for positive definiteness and
differentiability. The parameters $\ell$ and $\tau$ control the
length-scale and time-scale, respectively, of realizations (i.e.,
sample functions) of $u_i$. The parameter $\phi$, which we have
arbitrarily chosen to incorporate into $T_i$ rather than $X_i$,
controls the amplitude of realizations of $u_i$. Ideally, we want
realizations of $u_i$ to have a length-scale, time-scale, and
amplitude that resemble what we expect for the true transient
displacements. In Figure \ref{fig:PriorDemo}A, we show $C_{u_i}$ using
the squared exponential function $X_i$ and $T_i$ and the parameters
$\ell = 100$ km, $\tau = 10$ days, and $\phi = 1$ mm. A single
realization of $u_i$ corresponsing to that choice of covariance
function is shown in Figure \ref{fig:PriorDemo}B (See \citet[sec.
A3]{Rasmussen2006} for details on drawing realization from Gaussian
processes).

The covariance function for $u_i$ and one realizations
for $u_i$ are shown in Figure \ref{fig:PriorDemo} using the parameters
While the
squared exponential function is a commonly used covariance function
for GPR, it is not appropriate for every application. The appropriate
choice for $X_i$ and $T_i$ may vary depending on the geophysical
signal we are trying to describe. To keep this section sufficiently
general, we hold off on specifying $X_i$ and $T_i$ until Section
\ref{sec:SignalModel}, where we estimate transient strain from slow
slip events in the Pacific Northwest.

>>>>

We provide an example to give the prior on transient displacements a
more tangible meaning. we can use a squared exponential function for
$X_i$ and $T_i$,
\begin{equation}\label{eq:ExampleCov}
X_i(\pos,\pos') = \exp\left(\frac{-||\pos - \pos'||_2^2}{2\ell^2}\right), \ \ \ \ 
T_i(t,t') = \phi^2 \exp\left(\frac{-|t - t'|^2}{2\tau^2}\right),
\end{equation}
which satisfies our requirements for positive definiteness and
differentiability. The parameters $\ell$ and $\tau$ control the
length-scale and time-scale, respectively, of realizations (i.e.,
sample functions) of $u_i$. The parameter $\phi$, which we have
arbitrarily chosen to incorporate into $T_i$ rather than $X_i$,
controls the amplitude of realizations of $u_i$. Ideally, we want
realizations of $u_i$ to have a length-scale, time-scale, and
amplitude that resemble what we expect for the true transient
displacements. In Figure \ref{fig:PriorDemo}A, we show $C_{u_i}$ using
the squared exponential function for $X_i$ and $T_i$ and the
parameters $\ell = 100$ km, $\tau = 10$ days, and $\phi = 1$ mm. A
single realization of $u_i$ corresponsing to that choice of covariance
function is shown in Figure \ref{fig:PriorDemo}B (See \citet[sec.
A3]{Rasmussen2006} for details on drawing realization from Gaussian
processes). While the squared exponential function is a commonly used
covariance function for GPR, it is not appropriate for every
application. The appropriate choice for $X_i$ and $T_i$ may vary
depending on the geophysical signal we are trying to describe. To keep
this section sufficiently general, we hold off on specifying $X_i$ and
$T_i$ until Section \ref{sec:SignalModel}, where we estimate transient
strain from slow slip events in the Pacific Northwest.
